Tail-indices and scale parameters of returns series

### 2017-04-05 papers/FX/draft.tex
Revised my bib file. Corrected the citations. Updated the proof.

\cite{barndorff:shephard:2001} and Eberlein \cite{eberlein:2001} favor ``semi-heavy'' tails, i.e.,
tails which are comparable with those of a gamma \ds . On the other
hand, tails of returns have been studied in great detail 
in the extreme value community. Among extreme value specialists
there is general agreement that returns $X_t$ have tails of power-law-type, i.e.,

@@

\P(X_t>x)\sim c_+ \,x^{\alpha_{\rm up}}\quad\mbox{and}\quad \P(X_t<-x)\sim c_-\,x^{-\alpha_{\rm low}}\,,\quad\xto\,,

@@

al. \cite{embrechts:klueppelberg:mikosch:1997}, Jansen and de Vries

@@

al. \cite{embrechts:klueppelberg:mikosch:1997}, Chapter 3. In this

@@

(1991) \cite{gul1991theory}. The Gul paper derives the DA from first principles (axiomatic).

@@

see Embrechts et al. \cite{embrechts:klueppelberg:mikosch:1997}, de

@@

see Embrechts et al. \cite{embrechts:klueppelberg:mikosch:1997},

@@

\cite{drees:resnick:how to make a Hill plot}. In Figure~\ref{fig:1},

@@

al. \cite{embrechts:klueppelberg:mikosch:1997} for illustrations 

@@

Rootz\'en \cite{drees:rootzen:???} show that the \asy\ variance of the

@@

For convenience, we denote the scale parameter by $A$. It is the
constant $J_*(0)$ in the Taylor expansion \eqref{eq:scale_parameter}.
Hill \cite{hill1975simple} put forward an estimator of $A$ using his
tail index  estimator:
\[
\hat A = {k \over n} X_{(k+1)}^{\hat \alpha}
\]
where $X_{(k+1)}$ is the $(k+1)$-th upper order statistic of the
sequence $X_t$ as defined in section\ref{sec:Hill}. $\hat \alpha$
is the Hill tail index estimator.
Estimates of $A$ of the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index are computed
using this method. The results are shown in figure
\ref{fig:sectors_parameters}, along with estimates obtained
using the hybrid method described in section
\ref{sec:hybrid_estimation}.

@@

Hoga \cite{Hoga2017} proposed his test for a time series
$\{X_i\}_{i=1}^n$ with tail functions
$\bar F_i(\cdot)$, i.e. $\P(X_i > x) = \bar F_i(x)$. The null
hypothesis is
\begin{hypothesis}
  $\mathcal H_0$: For a given $p$, $\exists t^* \in [t_0, 1 - t_0]$
  such that
  \[
  \bar F_1^{-1}(p) = \bar F_2^{-1}(p) = \cdots =
  \bar F_{\floor{t^* n}}^{-1}(p) \neq
  \bar F_{\ceil{t^* n}}^{-1}(p) = \cdots = F_n^{-1}(p)
  \]
\end{hypothesis}
where $t_0 \in (0, 1/2)$. The alternative hypothesis is that no such
$t^*$ exists. Hoga proposed the following test statistics:
\[
Q_1 = \sup_{t \in [t_0, 1 - t_0]}
\left\{
  {
    \left[
      t (1 - t) \ln\left(
      \hat x_p(0, t)
      \over
      \hat x_p(t, 1)
      \right)
    \right]^2
    \over
    \int_{t_0}^t
    \left[
      s \ln \left(
      \hat x_p(0, s)
      \over
      \hat x_p(0, t)
      \right)
    \right]^2 ds
    +
    \int_{t}^{1 - t_0}
    \left[
      (1 - s) \ln \left(
      \hat x_p(s, 1)
      \over
      \hat x_p(t, 1)
      \right)
    \right]^2 ds
  }
\right\}
\]
Under the null hypothesis, Hoga showed that as $n \to \infty$,
\begin{equation}
  \label{eq:Q1_distr}
  Q_1 \overset{d}{\to}
  \sup_{t \in [t_0, 1 - t_0]} q_t
\end{equation}
where
\[
q_t = 
  {
    [W(t) - t W(1)]^2
    \over
    \int_{t_0}^t [W(s) - {s \over t}W(t)]^2 ds
    +
    \int_{t}^{1 - t_0}
    \left[
      W(1) - W(s) - {1 - s \over 1 - t}
      (W(1) - W(t))
      \right]^2 ds
  }
\]
$W(t)$ with $t \in (0, 1)$ is a standard Brownian motion.

When applied to our problem, We would like to test, first of all,
whether there is a change of tail index in each of two 
series and, if there is no change in either series, whether the two
series have the same tail index. Obviously, for either question, if
the tail index changes, the extreme quantile will change.
For the first question, Hoga's test is directly applicable; for the
second, we concatenate the two series before applying the
test.

Figure \ref{fig:Hoga_Single} shows the test statistics of
stocks in the ``Energy'' and ``Consumer Staples'' sectors of the S\&P
500 index. The null hypothesis here is that the tail index remains the
same througout the selected period of time.
\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]
    {Hoga_Energy_Single.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]
    {Hoga_Consumer_Staples_Single.pdf}
  \end{minipage}
  \caption{Hoga Test Statistics of stocks in the ``Energy'' and
    ``Consumer Staples'' sectors of S\&P 500. The green, blue and red
    lines are, respectively the 85\%, 90\% and 95\% quantiles of the
    distribution of \eqref{eq:Q1_distr}}.
  \label{fig:Hoga_Single}
\end{figure}

@@

Also of concern is the distribution of the test statistic under the
null hypothesis. This distribution is only known asymptotically (given
in equation \eqref{eq:Q1_distr}) when the sample size tends to
infinity. The rate at which the finite-sample distribution tends to
\eqref{eq:Q1_distr} is unclear. To find out more about this issue, we
draw samples from the Student's t(3) and t(4) distributions and
compare the empirical distribution of the test statistic $Q_1$ with the
empirical distribution of \eqref{eq:Q1_distr}, which we also obtain by
simulating the Brownian motion $W(t)$. The empirical density functions
are shown in figure \ref{fig:Q1_distr}.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Hoga_AsymptoticDistribution.pdf}
  \caption{Comparison of the asymptotic distribution with empirical
    distribution of $Q_1$ obtained from Student's t samples. The t
    samples have the same size as the S\&P sectors' data, namely 1304
    observations.}
  \label{fig:Q1_distr}
\end{figure}
As seen in the figure, the asymptotic distribution \eqref{eq:Q1_distr}
assigns significantly more mass to the tail than do the empirical
distributions of size 1304. Table \ref{tab:HogaAsymptotic} lists a few
quantiles of these distributions.
\begin{table}[htb!]
  \centering
  \begin{tabular}{c|c|c|c|c}
    & \multicolumn{4}{c}{Quantiles} \\
    \hline
    Distribution & 80\% & 85\% & 90\% & 95\% \\
    \hline
    Asymptotic & 47.48 & 59.61 & 78.90 & 113.12 \\
    t(3) empirical & 23.30 & 28.27 & 35.04 & 46.75 \\
    t(4) empirical & 25.76 & 31.13 & 38.81 & 56.32
  \end{tabular}
  \caption{Quantiles of the asymptotic and empirical test statistic
    distributions}
  \label{tab:HogaAsymptotic}
\end{table}

\section{Review of multivariate GARCH models:
  same tail index or not}
\label{sec:2}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).

In contrast, several other multivariate volatility models imply, in
general, different tail indices for different series. For example, the
Constant Conditional Correlation (CCC-) GARCH model of Bollerslev
(1990) \cite{bollerslev1990modelling} specifies, for a $d$-dimensional
series $\vec X_t$
\begin{eqnarray}
  \cov(X_{i,t}, X_{j,t}) &=& \sqrt{h_{i,t} h_{j,t}} \rho_{i,j}
  \nonumber \\
  h_{i,t} &=& \omega_i + \sum_{l=1}^q A_{i,l} X_{i, t-l}^2 +
  \sum_{l=1}^p B_{i,l} h_{i, t-l} \label{eq:CCC-GARCH}
\end{eqnarray}
Consider the simple case when $p=q=1$. Assume
$X_{i, t} = \sqrt h_{i,t} Z_{i,t}$, $Z_{i, t}$ are iid for
all $t \in \mathbb Z$, and $\P(|Z_{i,t}| > u)/\P(\sqrt h_{i,t} > u) \to 0$ as
$u \to \infty$. Then the tail index of the stationary distribution of
$X_{i,t}$, call it $\kappa_i$, is given by
\[
\E (A_{i, 1} Z^2 + B_{i, 1})^{\kappa_i / 2} = 1
\]
where $Z \overset{d}{=} Z_{i,t}$.
Provided $(A_{i,1}, B_{i,1}) \neq (A_{j,1}, B_{j,1})$, it is clear
$\kappa_i \neq \kappa_j$.

As an extension to the CCC-GARCH model, Jeantheau (1998)
\cite{jeantheau1998strong} proposed his Extended CCC-GARCH by
modifying \eqref{eq:CCC-GARCH} to
\begin{equation}
  \label{eq:ECCC-GARCH}
  \vec h_t =
  \sum_{l=1}^q \mathbf A_{l} (\vec X_{t-l} \odot \vec X_{t-l})
  +
  \sum_{l=1}^p \mathbf B_{l} \vec h_{t-l}
  +
  \vec \omega
\end{equation}
where $\mathbf A_l$ and $\mathbf B_l$ are non-diagonal $d \times d$ matrices
and $\odot$ denotes element-wise multiplication. In the simple case $p=q=1$,
equation \eqref{eq:ECCC-GARCH} reduces to
\begin{eqnarray*}
  h_{i,t} &=&
  \sum_{j=1}^d A_{i,j} X_{j, t-1}^2
  + \sum_{j=1}^d B_{i,j} h_{j, t-1}
  + \omega_i
\end{eqnarray*}
or in vector form
\begin{eqnarray}
  \vec h_t &=& \left[
    \mathbf A \text{diag}(Z_{1, t-1}^2, \dots, Z_{d, t-1}^2) + \mathbf B
    \right] \vec h_{t-1} + \vec \omega
  \label{eq:ECCC-GARCH2}
\end{eqnarray}
On appropriate conditions, \eqref{eq:ECCC-GARCH2} implies the
components of $\vec h_t$ are jointly regularly varying with some index
$\kappa$ as $t \to \infty$. This is a direct result of the Kesten-Goldie
theorem (cf. Kesten (1973)\cite{Kesten1973}). Thus all series under
consideration have the same tail index $\kappa$.

@@

\section{Generalized disappointment aversion}
\label{sec:3}
Routledge and Zin (2010) \cite{routledge2010generalized} define the GDA
preferences over discrete states in their formula (2). A slight extension
is to consider a continuum of possible states. Suppose the state variable
$C$ is continuously supported on $(0, \infty)$ and has distribution
function $G(\cdot)$. The utility function of an agent exhibiting GDA
preferences reads
\begin{equation}
  u(v)= \E u(C) - b \int_{0}^{\delta v}
  \left[ u(\delta v) - u(x) \right] dG(x)\label{11}%
\end{equation}
where $\delta > 0$, and $v>0$. Equivalently
\begin{equation}
  \label{eq:xxie0}
  u(v) = \E u(C) - b \E[u(\delta v) - u(C); C < \delta v]
\end{equation}
Here $v$ can be thought of as the certainty payoff equivalent to the
risky payoff $C$. Note that when $b=0$, 
preferences are expected utility; when $\delta=1$ and $b>0$,
preferences follow Gul's (1991) original disappointment aversion.
An agent guided by this utility function will seek to maximize $u(v)$.

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    {\partial \over \partial \theta}\left[
      F(b) - F(a)
    \right] = 0 \\
    \left| \frac{\pd f(x, \theta)}{\pd \theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the 2nd case of
    lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}
Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C(X) = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q = q(r, \phi) &:=& \ln \left( {
      \delta v - (1 - \phi) e^r
      \over
      \phi
    } \right) = \ln\left(
    e^r + {\delta v - e^r \over \phi}
  \right)
\end{eqnarray*}
Note $C < \delta v$ implies $X < q$. Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher return from the risky asset than he is guarranteed from the
riskless bond. In our notation, this means $\delta v > e^r$, which
implies $q(r, \phi) > r > 0$. The right-hand-side of
\eqref{eq:functional} is a functional of $\phi$ and of the distribution
function of $X$ via \eqref{eq:xxie1}. For convenience we denote it
$\mathcal U(\cdot, \cdot)$, i.e.
\begin{equation}
  \label{eq:U_functional}
  \mathcal U(F, \phi)
  = 
  \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\end{equation}
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\begin{equation}
  \label{eq:G_functional}
  G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)  
\end{equation}

>>>>

\cite{barndorff:shephard:2001} and Eberlein \cite{eberlein:2001} favor
``semi-heavy'' tails, i.e., tails which are comparable with those of a
gamma \ds . On the other hand, tails of returns have been studied in
great detail in the extreme value community. Among extreme value
specialists there is general agreement that returns $X_t$ have tails
of power-law-type, i.e.,

@@

\P(X_t>x)\sim c_+ \,x^{-\alpha_{\rm up}}\quad\mbox{and}\quad
\P(X_t<-x)\sim c_-\,x^{-\alpha_{\rm low}}\,,\quad\xto\,,

@@

al. \cite{Embrechts1997}, Jansen and de Vries

@@

al. \cite{Embrechts1997}, Chapter 3. In this

@@

 \cite{gul1991theory}. The Gul paper derives the DA from first principles (axiomatic).

@@

see Embrechts et al. \cite{Embrechts1997}, de

@@

see Embrechts et al. \cite{Embrechts1997},

@@

\cite{drees:resnick:2000}. In Figure~\ref{fig:1},

@@

al. \cite{Embrechts1997} for illustrations 

@@

Rootz\'en \cite{drees:rootzen:2010} show that the \asy\ variance of the

@@

For convenience, we denote the scale parameter by $A$.
%% It is the constant $J_*(0)$ in the Taylor expansion \eqref{eq:scale_parameter}.
Hill \cite{hill1975simple} put forward an estimator of $A$ using his
tail index  estimator:
\[
\hat A = {k \over n} X_{(k+1)}^{\hat \alpha}
\]
where $X_{(k+1)}$ is the $(k+1)$-th upper order statistic of the
sequence $X_t$ as defined in section\ref{sec:Hill}. $\hat \alpha$
is the Hill tail index estimator.
Estimates of $A$ of the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index are computed
using this method. The results are shown in figure
\ref{fig:sectors_parameters}, along with estimates obtained
using the hybrid method described in section
\ref{sec:hybrid_estimation}.

@@

Hoga \cite{Hoga2017} proposed his test for a time series
$\{X_i\}_{i=1}^n$ with tail functions
$\bar F_i(\cdot)$, i.e. $\P(X_i > x) = \bar F_i(x)$. The null
hypothesis is
\begin{hypothesis}
  $\mathcal H_0$: For a given $p$ and all $1 \leq i < j \leq n$,
  $F_i^{-1}(p) = F_j^{-1}(p)$
\end{hypothesis}
while the alternative is $\exists t^* \in [t_0, 1 - t_0]$ such that
\[
\bar F_1^{-1}(p) = \bar F_2^{-1}(p) = \cdots =
\bar F_{\floor{t^* n}}^{-1}(p) \neq
\bar F_{\ceil{t^* n}}^{-1}(p) = \cdots = F_n^{-1}(p)
\]
where $t_0 \in (0, 1/2)$ and $\hat x_p(s, t)$ is the Weissman
estimator applied to the partial series
$X_{\ceil{ns}}, \dots, X_{\floor{nt}}$ using $\ceil{k(t - s)}$
upper-order statistics. See Embrechts, Kl\"uppelberg and T.Mikosch
\cite{Embrechts1997}, p.347.

Hoga proposed the following test statistics:
\[
Q_1 = \sup_{t \in [t_0, 1 - t_0]}
\left\{
  {
    \left[
      t (1 - t) \ln\left(
      \hat x_p(0, t)
      \over
      \hat x_p(t, 1)
      \right)
    \right]^2
    \over
    \int_{t_0}^t
    \left[
      s \ln \left(
      \hat x_p(0, s)
      \over
      \hat x_p(0, t)
      \right)
    \right]^2 ds
    +
    \int_{t}^{1 - t_0}
    \left[
      (1 - s) \ln \left(
      \hat x_p(s, 1)
      \over
      \hat x_p(t, 1)
      \right)
    \right]^2 ds
  }
\right\}
\]
Under the null hypothesis and suitable dependence conditions, Hoga
showed that as $n \to \infty$,
\begin{equation}
  \label{eq:Q1_distr}
  Q_1 \overset{d}{\to}
  \sup_{t \in [t_0, 1 - t_0]} q_t
\end{equation}
where
\[
q_t = 
  {
    [W(t) - t W(1)]^2
    \over
    \int_{t_0}^t [W(s) - {s \over t}W(t)]^2 ds
    +
    \int_{t}^{1 - t_0}
    \left[
      W(1) - W(s) - {1 - s \over 1 - t}
      (W(1) - W(t))
      \right]^2 ds
  }
\]
$W(t)$ with $t \in (0, 1)$ is a standard Brownian motion.

When applied to our problem, we would like to test, first of all,
whether there is a change of tail index in each of two 
series and, if there is no change in either series, whether the two
series have the same tail index. Obviously, for either question, if
the tail index changes, the extreme quantile will change.
For the first question, Hoga's test is directly applicable; for the
second, we concatenate the two series before applying the
test.

Figure \ref{fig:Hoga_Single} shows the test statistics of
stocks in the ``Energy'' and ``Consumer Staples'' sectors of the S\&P
500 index. The null hypothesis here is that the extreme quantile
remains the same througout the selected period of time.
\begin{figure}[htb!]
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]
    {Hoga_Energy_Single.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]
    {Hoga_Consumer_Staples_Single.pdf}
  \end{minipage}
  \caption{Hoga Test Statistics of stocks in the ``Energy'' and
    ``Consumer Staples'' sectors of S\&P 500. The green, blue and red
    lines are, respectively the 85\%, 90\% and 95\% quantiles of the
    distribution of \eqref{eq:Q1_distr}}.
  \label{fig:Hoga_Single}
\end{figure}

@@

Also of concern is the distribution of the test statistic under the
null hypothesis. This distribution is only known asymptotically (given
in equation \eqref{eq:Q1_distr}) when the sample size tends to
infinity. The rate at which the finite-sample distribution tends to
\eqref{eq:Q1_distr} is unclear. To find out more about this issue, we
draw samples from the Student's t(3) and t(4) distributions and
compare the empirical distribution of the test statistic $Q_1$ with the
empirical distribution of \eqref{eq:Q1_distr}, which we also obtain by
simulating the Brownian motion $W(t)$. The empirical density functions
are shown in figure \ref{fig:Q1_distr}.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Hoga_AsymptoticDistribution.pdf}
  \caption{Comparison of the asymptotic distribution with empirical
    distribution of $Q_1$ obtained from Student's t samples. Each t
    sample has the same size as the S\&P sectors' data, namely 1304
    observations.}
  \label{fig:Q1_distr}
\end{figure}
As seen in the figure, the asymptotic distribution \eqref{eq:Q1_distr}
assigns significantly more mass to the tail than do the empirical
distributions of size 1304. Table \ref{tab:HogaAsymptotic} lists a few
quantiles of these distributions.
\begin{table}[htb!]
  \centering
  \begin{tabular}{c|c|c|c|c}
    & \multicolumn{4}{c}{Quantiles} \\
    \hline
    Distribution & 80\% & 85\% & 90\% & 95\% \\
    \hline
    Asymptotic & 47.48 & 59.61 & 78.90 & 113.12 \\
    t(3) empirical & 23.30 & 28.27 & 35.04 & 46.75 \\
    t(4) empirical & 25.76 & 31.13 & 38.81 & 56.32
  \end{tabular}
  \caption{Quantiles of the asymptotic and empirical test statistic
    distributions}
  \label{tab:HogaAsymptotic}
\end{table}

\section{Review of multivariate GARCH models:
  same tail index or not}
\label{sec:2}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al 
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch 
\cite{andersen2009handbook}).

In contrast, several other multivariate volatility models imply, in
general, different tail indices for different series. For example, the
Constant Conditional Correlation (CCC-) GARCH model of Bollerslev
\cite{bollerslev1990modelling} specifies, for a $d$-dimensional
series $\vec X_t$
\begin{eqnarray}
  \cov(X_{i,t}, X_{j,t}) &=& \sqrt{h_{i,t} h_{j,t}} \rho_{i,j}
  \nonumber \\
  h_{i,t} &=& \omega_i + \sum_{l=1}^q A_{i,l} X_{i, t-l}^2 +
  \sum_{l=1}^p B_{i,l} h_{i, t-l} \label{eq:CCC-GARCH}
\end{eqnarray}
Consider the simple case when $p=q=1$. Assume
$X_{i, t} = \sqrt h_{i,t} Z_{i,t}$, $Z_{i, t}$ are iid for
all $t \in \mathbb Z$, and $\P(|Z_{i,t}| > u)/\P(\sqrt h_{i,t} > u) \to 0$ as
$u \to \infty$. Then the tail index of the stationary distribution of
$X_{i,t}$, call it $\kappa_i$, is given by
\[
\E (A_{i, 1} Z^2 + B_{i, 1})^{\kappa_i / 2} = 1
\]
where $Z \overset{d}{=} Z_{i,t}$. It is clear $\kappa_i \neq \kappa_j$
except for special values of $A_i, B_i$ and $A_j, B_j$.

As an extension to the CCC-GARCH model, Jeantheau 
\cite{jeantheau1998strong} proposed his Extended CCC-GARCH by
modifying \eqref{eq:CCC-GARCH} to
\begin{equation}
  \label{eq:ECCC-GARCH}
  \vec h_t =
  \sum_{l=1}^q \mathbf A_{l} (\vec X_{t-l} \odot \vec X_{t-l})
  +
  \sum_{l=1}^p \mathbf B_{l} \vec h_{t-l}
  +
  \vec \omega
\end{equation}
where $\mathbf A_l$ and $\mathbf B_l$ are non-diagonal $d \times d$ matrices
and $\odot$ denotes element-wise multiplication. In the simple case $p=q=1$,
equation \eqref{eq:ECCC-GARCH} reduces to
\begin{eqnarray*}
  h_{i,t} &=&
  \sum_{j=1}^d A_{i,j} X_{j, t-1}^2
  + \sum_{j=1}^d B_{i,j} h_{j, t-1}
  + \omega_i
\end{eqnarray*}
or in vector form
\begin{eqnarray}
  \vec h_t &=& \left[
    \mathbf A \text{diag}(Z_{1, t-1}^2, \dots, Z_{d, t-1}^2) + \mathbf B
    \right] \vec h_{t-1} + \vec \omega
  \label{eq:ECCC-GARCH2}
\end{eqnarray}
On appropriate conditions, \eqref{eq:ECCC-GARCH2} implies the
components of $\vec h_t$ are jointly regularly varying with some index
$\kappa$ as $t \to \infty$. This is a direct result of the Kesten-Goldie
theorem (cf. Kesten \cite{Kesten1973}). Thus all series under
consideration have the same tail index $\kappa$.

@@

\section{Generalized disappointment aversion}
\label{sec:3}
Routledge and Zin \cite{routledge2010generalized} define the GDA
preferences over discrete states in their formula (2). A slight extension
is to consider a continuum of possible states. Suppose the state variable
$C$ is continuously supported on $(0, \infty)$ and has distribution
function $G(\cdot)$. The utility function of an agent exhibiting GDA
preferences reads
\begin{equation}
  u(v)= \E u(C) - b \int_{0}^{\delta v}
  \left[ u(\delta v) - u(x) \right] dG(x)\label{11}%
\end{equation}
where $\delta > 0$, $v>0$ and $b > 0$. Equivalently
\begin{equation}
  \label{eq:xxie0}
  u(v) = \E u(C) - b \E[u(\delta v) - u(C); C < \delta v]
\end{equation}
Here $v$ can be thought of as the certainty payoff equivalent to the
risky payoff $C$. Note that when $b=0$, 
preferences are expected utility; when $\delta=1$ and $b>0$,
preferences follow Gul's original disappointment aversion.
An agent guided by this utility function will seek to maximize $u(v)$.

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
increasing and concave. Before proceeding any further, it is worth
stating the following simple observation:
\begin{lemma} \label{lemma:I}
  Assume distribution function $F(x; \theta)$ parameterized by
  $\theta$ is defined on $x \in (a, b)$, $a, b \in \mathbb R \cup
  \{-\infty, \infty\}$, and in addition $F(x; \theta)$ has density
  function $f(x; \theta)$. Assume function $h(\cdot)$ is defined on
  $(a, b)$, $X \sim F$, $\text{supp}(X) = (a,b)$,
  $\E h(X) < \infty$ and
  \begin{eqnarray*}
    \left| \frac{\pd f(x, \theta)}{\pd \theta} \right| < \infty
    \quad \forall x \in (a, b)
  \end{eqnarray*}
  \begin{enumerate}
  \item If $h(\cdot)$ is decreasing and $\exists x_0 \in (a, b)$ such that
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(a, x_0)$ while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \item If $h(\cdot)$ is increasing and $\exists x_0 \in (a, b)$ such that 
    $\frac{\pd f}{\pd \theta}(x_0; \theta) < 0$ on $(a, x_0)$  while
    $\frac{\pd f}{\pd \theta}(x_0; \theta) > 0$ on $(x_0, b)$, then
    \[
    \frac{\pd \E h(X)}{\pd \theta} > 0
    \]
  \end{enumerate}
\end{lemma}
\begin{remark}
  \label{remark:I}
  Two other cases follow trivially from lemma \ref{lemma:I}:
  \begin{enumerate}
  \item If $h(\cdot)$ is increasing and $\frac{\pd f}{\pd \theta}$
    satisfies the
    same conditions of the 1st case of lemma \ref{lemma:I},
    $\frac{\pd \E h(X)}{\pd \theta} < 0$. This immediately follows
    from applying 1st case of lemma \ref{lemma:I} to $-h(\cdot)$.
  \item By the same argument, if $h(\cdot)$ is decreasing and
    ${\pd f \over \pd \theta}$ satisfies the same conditions of the 2nd case of
    lemma \ref{lemma:I}, ${\pd \E h(X) \over \pd \theta} < 0$.
  \end{enumerate}
\end{remark}
Now for simplicity we assume the investor initially has one unit of
wealth. Let $r > 0$ be the return on the risk free state bond and $X$
be the return on equity. Portfolio weights are $\left(1-\phi\right)$
and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  C(X) = (1 - \phi) e^r + \phi e^X
\end{equation}
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q = q(r, \phi) &:=& \ln \left( {
      \delta v - (1 - \phi) e^r
      \over
      \phi
    } \right) = \ln\left(
    e^r + {\delta v - e^r \over \phi}
  \right)
\end{eqnarray*}
Note $C < \delta v$ implies $X < q$. Naturally, if an agent invests in
a risky asset instead of a riskless bond, he expects to obtain a
higher return from the risky asset than he is guarranteed from the
riskless bond. In our notation, this means $\delta v > e^r$, which
implies $q(r, \phi) > r > 0$. The right-hand-side of
\eqref{eq:functional} is a functional of $\phi$ and of the distribution
function of $X$ via \eqref{eq:xxie1}. For convenience we denote it
$\mathcal U(\cdot, \cdot)$, i.e.
\begin{equation}
  \label{eq:U_functional}
  \mathcal U(F, \phi)
  = 
  \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\end{equation}
In the rest of this section, we use $F(\cdot)$ to denote the
distribution function of $X$ and use $f(\cdot)$ to denote its density
function. Let
\begin{equation}
  \label{eq:G_functional}
  G(F) = \max_{0 < \phi \leq 1} \mathcal U(F, \phi)  
\end{equation}
